Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-09-10 reproducing_registered_reports.Rmd
submission version

abstract: |
  Ongoing technological developments have made it easier than ever before for scientists to share their data, materials, and analysis code. Sharing data and analysis code makes it easier for other researchers to re-use or check published research. These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean. Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved. We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018. Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles. For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles. Although the articles that shared both data and code (35 out of 62, or 56%) and articles that could be computationally reproduced (20 out of 35, or 57%) was relatively high compared to other studies, there is clear room for improvement. We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience; SG ran all MATLAB and Python code). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results. All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). (It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)

>>>>

abstract: |
  Ongoing technological developments have made it easier than ever before for scientists to share their data, materials, and analysis code. Sharing data and analysis code makes it easier for other researchers to re-use or check published research. These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean. Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved. We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018. Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles. For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles. Although the articles that shared both data and code (35 out of 62, or 56%) and articles that could be computationally reproduced (20 out of 35, or 57%) was relatively high compared to other studies, there is clear room for improvement. We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG, NC and DL had more experience; SG ran all MATLAB and Python code). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results. All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). (It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)

### 2019-09-10 reproducing_registered_reports.tex
submission version

\abstract{
Ongoing technological developments have made it easier than ever before for scientists to share their data, materials, and analysis code. Sharing data and analysis code makes it easier for other researchers to re-use or check published research. These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean. Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved. We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018. Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles. For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles. Although the articles that shared both data and code (35 out of 62, or 56\%) and articles that could be computationally reproduced (20 out of 35, or 57\%) was relatively high compared to other studies, there is clear room for improvement. We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience; SG ran all MATLAB and Python code). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results. All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). (It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)

>>>>

\abstract{
Ongoing technological developments have made it easier than ever before for scientists to share their data, materials, and analysis code. Sharing data and analysis code makes it easier for other researchers to re-use or check published research. These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean. Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved. We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018. Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles. For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles. Although the articles that shared both data and code (35 out of 62, or 56\%) and articles that could be computationally reproduced (20 out of 35, or 57\%) was relatively high compared to other studies, there is clear room for improvement. We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG, NC and DL had more experience; SG ran all MATLAB and Python code). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results. All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). (It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)
